Clinical Data Model

### 2024-11-05 08_Msystems_resubmission/00_machine_learning_analysis/model_workflow.qmd

# Only doing a simple logistic regression since a tree-based model would most certainly overfit
log_reg <- logistic_reg(
  mixture = 1 # Lasso regression, using this to hopefully get rid of a lot of features that don't matter (sets coefficients of nonimportant features to 0, effectively removing them)
  penalty = tune() # testing a few different penalty values
) %>% 
  set_engine("glmnet") 
```

>>>>

# Only doing a simple logistic regression since a tree-based model would most certainly overfit
log_reg <- logistic_reg(
  mixture = 1, # Lasso regression, using this to hopefully get rid of a lot of features that don't matter (sets coefficients of nonimportant features to 0, effectively removing them)
  penalty = tune() # testing a few different penalty values
) %>% 
  set_engine("glmnet") 
```
